---
title: "Kite CORT - Assignment 5"
author: "M. Richard"
date: "October 2, 2019"
output: html_document
---

Lopez-Jimenez, L., J. Blas, A. Tanferna, S. Cabezas, T. Marchant, F. Hiraldo and F. Sergio. 2016. Ambient temperature, body condition and sibling rivalry explain feather corticosterone levels in developing black kites. Functional Ecology 30:605-613. 

Authors' hypothesis: do feather corticosterone (CORT) levels reflect the energetic demands of black kite nestlings during their development?

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
library(MuMIn)
library(ggplot2)
library(dplyr)
library(readr)
library(tidyr)
library(knitr)

kites <- read_csv("KiteCort.csv")
kites <- select(kites, -'BROOD ORDER')

colnames(kites)[colnames(kites)=="MEAN TEMPERATURE"] <- "Temperature"
colnames(kites)[colnames(kites)=="AGE        (days)"] <- "Age"
colnames(kites)[colnames(kites)=="FEATHER CORT (ng/mm)"] <- "CORT"
colnames(kites)[colnames(kites)=="BODY CONDITION"] <- "Body"
colnames(kites)[colnames(kites)=="NEST ID"] <- "Nest ID"
```
Sex, brood order, and year were categorical variables. 
Body condition, territory quality, hatch date, age, and ambient temperature are predictor variables. 
```{r check for co-linearity}
pairs(kites[,3:5], lower.panel = NULL)
```





There does not appear to be any co-linearity between variables. 


```{r message=FALSE, warning=FALSE, paged.print=FALSE}
kite_global <- lm(CORT ~ Age + Body + Temperature , data = kites)
options(na.action = "na.fail")
results<- dredge(kite_global)
results
```

The model 8 including age, body condition, and average temperature had the highest AICc value with the highest weight. 

```{r subset to best models}
subset(results, delta <5)

```

Subsetting the data doesn't help to narrow down the top models because there is only one model that is logical given the delta and weight values.

```{r calculate variable weights}
importance(results)
```

Looking at the variable weights confirms model 8 as the best model with all three variables having a highest weight possible, 1. 

This partically confirms the researchers findings in terms of important varaibles. However, they only provided a partial data set excluding the variables territory quality and hatch date.  
Researchers concluded that CORT increase with decreasing temperature and decreasing body temperature, and CORT levels decreased with age in nestlings with siblings. 